\subsection{Introduction}
  \input{substepping-basics.tex}

\subsection{Method}
  \input{substepping-steps.tex}

\subsection{Results (Slimani \& al. (2025))}
  \input{substepping-examples.tex}

\subsection{Conclusions (Slimani \& al. (2025))}
\begin{frame}
  \frametitle{Slimani \& al. (2025)}
  \framesubtitle{Conclusions}
  \begin{itemize}
    \item Advected subdomains improve steadiness and HAZ accuracy,
    but are not robust: for realistic scan paths (direction changes,
    overlaps), the advected subdomain pollutes the accumulated thermal
    field from previous tracks.

    \item Substepping is more robust: it is largely insensitive to scan-path
    complexity and directly targets the localized time-scale disparity in
    LPBF via a fast/slow partitioning.

    \item The proposed fully-staggered Robin--Robin substepper achieves
    accuracy comparable to the Dirichlet substepper of \cite{hodge2021},
    at slightly lower computational cost.

    \item The Dirichlet substepper is sensitive to predictor choice;
    a diffusion-only predictor improves stability and accuracy at large
    \(\Delta t_s\).

    \item Substepping speed-up is controlled by the fast/slow DOF ratio:
    increasing \(\Delta t_s\) enlarges the fast domain \(\Omega_f\),
    which increases the number of fast DOFs and can ultimately reduce
    the achievable speed-up despite fewer macro-steps.

    \item With first-order time integration in \(\Omega_s\), it is difficult
    to increase \(\Delta t_s\) beyond \(\sim 5\,T_{hs}\), as
    slow-scale diffusion becomes under-resolved.
  \end{itemize}
  \end{frame}
